Control Script for SCOPE data

### 2023-05-04 untargeted/output_control.Rmd
Converting purl chunks to TRUE

```{r setup, include=FALSE, purl=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = TRUE, purl = FALSE)
options(dplyr.summarise.inform=F)
options(pillar.sigfig=10)
suppressPackageStartupMessages(library(tidyverse))
library(data.table)
library(pbapply)
library(RaMS)

@@

cruise_metadata <- read.csv("../metadata/made_data/file_metadata.csv") %>%
  filter(cruise==!!cruise)

@@

```{r peakpicking, error=TRUE, purl=FALSE}
library(xcms)

@@

```{r deisoadduct, error=TRUE, purl=FALSE}
library(xcms)
xdata_filled <- readRDS(file = paste0(output_folder, "xdata_filled.rds"))
filled_peaks <- read.csv(file = paste0(output_folder, "filled_peaks.csv"))

@@

```{r assignformulae, purl=FALSE}
M_area_peaks <- read.csv(paste0(output_folder, "M_area_peaks.csv"))
feature_envelopes <- read.csv(paste0(output_folder, "feature_envelopes.csv"))
feature_data <- M_area_peaks %>%
  group_by(feature) %>%
  summarise(mzmed=median(mz), rtmed=median(rt), avg_area=mean(M_area))
stan_annotations <- read.csv(paste0(output_folder, "stan_annotations.csv"))
# database_formulae <- readRDS("unique_formulae.rds") %>%
#   gsub(pattern = "\\+.?", replacement = "")
database_formulae <- unique(readRDS("../metadata/raw_data/hmdb_formulae.rds"))

@@

```{r assignids}
filled_peaks <- read.csv(paste0(output_folder, "filled_peaks.csv"))
feature_envelopes <- read.csv(paste0(output_folder, "feature_envelopes.csv"))
feature_data <- filled_peaks %>%
  group_by(feature) %>%
  summarise(mzmed=median(mz), rtmed=median(rt), avg_area=mean(M_area)) %>%
  left_join(feature_envelopes, by = "feature")
stan_annotations <- read.csv(paste0(output_folder, "stan_annotations.csv"))

>>>>

```{r setup, include=FALSE, purl=TRUE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = TRUE, purl=TRUE)
options(dplyr.summarise.inform=F)
options(pillar.sigfig=10)
suppressPackageStartupMessages(library(tidyverse))
library(data.table)
library(pbapply)
library(RaMS)

@@

cruise_metadata <- read.csv("../metadata/made_data/file_metadata.csv") %>%
  filter(cruise==!!cruise) %>%
  filter(polarity==!!polarity)

@@

```{r peakpicking, error=TRUE, purl=TRUE}
library(xcms)

@@

```{r deisoadduct, error=TRUE, purl=TRUE}
library(xcms)
xdata_filled <- readRDS(file = paste0(output_folder, "xdata_filled.rds"))
filled_peaks <- read.csv(file = paste0(output_folder, "filled_peaks.csv"))

@@

```{r assignformulae, purl=TRUE}
M_area_peaks <- read.csv(paste0(output_folder, "M_area_peaks.csv"))
feature_envelopes <- read.csv(paste0(output_folder, "feature_envelopes.csv"))
feature_data <- M_area_peaks %>%
  group_by(feature) %>%
  summarise(mzmed=median(mz), rtmed=median(rt), avg_area=mean(M_area))
stan_annotations <- read.csv(paste0(output_folder, "stan_annotations.csv"))
# database_formulae <- readRDS("unique_formulae.rds") %>%
#   gsub(pattern = "\\+.?", replacement = "")
database_formulae <- unique(readRDS("../metadata/raw_data/hmdb_formulae.rds"))

@@

```{r assignids, purl=FALSE}
filled_peaks <- read.csv(paste0(output_folder, "M_area_peaks.csv"))
feature_envelopes <- read.csv(paste0(output_folder, "feature_envelopes.csv"))
feature_data <- filled_peaks %>%
  group_by(feature) %>%
  summarise(mzmed=median(mz), rtmed=median(rt), avg_area=mean(M_area))
stan_annotations <- read.csv(paste0(output_folder, "stan_annotations.csv"))

want_stans <- c("MT_POS_FT0489", "MT_POS_FT0519", "MT_POS_FT0525", "MT_POS_FT0567", 
"MT_POS_FT0584", "MT_POS_FT0720", "MT_POS_FT0862", "MT_POS_FT0973", 
"MT_POS_FT0433", "MT_POS_FT0618", "MT_POS_FT0664", "MT_POS_FT0691", 
"MT_POS_FT0744", "MT_POS_FT0607", "MT_POS_FT0617", "MT_POS_FT1113", 
"MT_POS_FT1178")
feature_data <- feature_data %>% filter(feature%in%str_remove(want_stans, "MT_POS_"))
